\section{Noise free benchmark BBOB functions}

The noise free benchmark BBOB functions~\cite{hansen2010real} are a selected group of functions that we understand suits our objective to evaluate the performance of the tournament selection. That is because these collection of functions are intend to be more difficult than the problems that would be seen in practice, though these difficulties are believed to occur in continuous domain search. Also, all benchmark functions are scalable with the dimension. 


These functions can be separated in two groups given their complexity. The first group is composed by the unimodal functions while the second group is composed by the multimodal functions. Here we consider that unimodal functions are functions with only one local optimum (equal to the global optimum) while multimodal functions are functions has many local optimum (with one of them being the global optimum). 

The unimodal functions are: Ellipsoidal Function, Linear Slope, Atractive Sector Function,  Step Ellipsoidal Function, Rosenbrock Function - original, Rosenbrock Function - rotated, Discus Function, Bent Cigar Function, Sharp Ridge Function, and Different Powers Function.

While the multimodal functions are: Rastrigin Function, Weierstrass Function, Schaffers Function, Schaffers Function ,moderately ill-conditioned, Composite Griewank-Rosenbrock Function F8F2, Schwefel Function, Gallagher's Gaussian 101-me Peaks Function, Gallagher's Gaussian 21-hi Peaks Function, Katsuura Function, and Lunacek bi-Rastrigin Function.