\documentclass[sigconf, authordraft, anonymous]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{subcaption}
\usepackage[]{algorithm2e}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.1145/nnnnnnn.nnnnnnn}

% ISBN
\acmISBN{978-x-xxxx-xxxx-x/YY/MM}


%Conference
\acmConference[GECCO '18]{the Genetic and Evolutionary Computation
Conference 2018}{July 15--19, 2018}{Kyoto, Japan}
\acmYear{2018}
\copyrightyear{2018}

%\acmArticle{4}
\acmPrice{15.00}

\begin{document}
\title{Experimental Analysis of the Tournament Size on Genetic Algorithms}

\author{Yuri Lavinas}
\affiliation{\institution{University of Tsukuba}}
\email{yclavinas@gmail.com}

\author{Claus Aranha}
\affiliation{\institution{University of Tsukuba}}
\email{caranha@cs.tsukuba.ac.jp}

\author{Tetsuya Sakurai}
\affiliation{\institution{University of Tsukuba}}
\email{sakurai@cs.tsukuba.ac.jp}

\begin{abstract}
We perform an experimental study about the effect of the tournament
size parameter from the Tournament Selection operator. Tournament
Selection is a classic operator for Genetic Algorithms and Genetic
Programming. It is simple to implement and has only one control
parameter, the \emph{tournament size}. Even though it is commonly
used, most practitioners still rely on rules of thumb when choosing
the tournament size. For example, almost all works in the past 15
years use a value of 2 for the tournament size, with little reasoning
behind that choice. To understand the role of the tournament size, we
run a real-valued GA on 24 BBOB problems with 10, 20 and 40
dimensions. We also vary the crossover operator and the generational
policy of the GA. For each combination of the above factors we observe
how the quality of the final solution changes with the tournament
size. Our findings do not support the indiscriminate use of tournament
size 2, and recommend a more careful set up of this parameter.
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010257.10010293.10011809.10011812</concept_id>
<concept_desc>Computing methodologies~Genetic algorithms</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Genetic algorithms}

\keywords{Genetic Algorithm, Tournament Selection, Selection Schemes}


\maketitle

%\input{samplebody-conf}
\input{1_intro.tex}
\input{2_background.tex} 
\input{3_bbob.tex}
\input{4_experiment.tex}
\input{5_results.tex}
\input{6_conclusion.tex}


\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography} 

\end{document}
